The Country-level Impact of Educational Features on the Rate of Entrepreneurship - Data Gathering and Analysis

### 2014-11-13 GEMDataSource.Rmd
Update GEMDataSource.Rmd
Data Collection Comment

Regarding entrepreneurship, we intend to look into three dimensions. We intend to look at established entrepreneurship in the country, whether it is successful or not, nascent entrepreneurship (less than three months), again whether it is successful or not, and entrepreneurial intention. We may well observe different effects, studying them successively.

>>>>>>> d492a8dcde27e8a4480f0504d410e52e7c2d7e6e

>>>>

Regarding entrepreneurship, we intend to look into three dimensions. We intend to look at established entrepreneurship in the country, whether it is successful or not, nascent entrepreneurship (less than three months), again whether it is successful or not, and entrepreneurial intention. We will study them successively as we may well observe different effects.

### Conclusion

The impact of cultural factors in education on the rate of entrepreneurship in a given country is an important and under-researched topic that should be considered by policymakers constructing public education budgets. Through this project, we hope to encourage the consideration of these cultural factors by providing a qualitative and quantitative method for understanding the impact of these factors. Although several challenges remain to compiling the indexes discussed in this report, we are confident we can produce a helpful framework for examining and understanding these factors.

### References
